PEACE: {\underline P}arallel {\underline E}nvironment for {\underline A}ssembly and {\underline C}lustering of Gene {\underline E}xpression

### 2010-02-12 peace/papers/NAR_web_server_2009/paper.tex
Corrections to manuscript, as found by Jenna

Here we have presented {\sc Peace}, a stand-alone tool for the
high-throughput clustering of transcript fragments, managed through a
user friendly GUI that enables both local and remote instillation and
execution in sequential or parallel mode.  Based on a novel algorithm
for the clustering of the fragments by gene association, {\sc Peace}
shows significant improvement in sensitivity while increasing runtime
over the competing {\sc WCD} tool \cite{Hazelhurst08a}, and shows an
order of magnitude in improvement over the clustering preformed in the
course of assembly by the {\sc Cap3} tool \cite{Huang99}.

@@

In short: {\sc Peace} can out-preform existing fragment cluster tools
on fragment data.  By using the {\sc Peace} GUI, the user can easily
set up a first analysis of transcript distributions and set the user
up for a significant reduction in the overall time for assembly a
transcript from fragment transcript sequences.

>>>>

Here we have presented {\sc Peace}, a stand-alone tool for the
high-throughput clustering of transcript fragments, managed through a
user friendly GUI that enables both local and remote installation and
execution in sequential or parallel mode.  Based on a novel algorithm
for the clustering of the fragments by gene association, {\sc Peace}
shows significant improvement in sensitivity, without sacrificing  runtime,
over the competing {\sc WCD} tool \cite{Hazelhurst08a}, and shows an
order of magnitude in improvement over the clustering preformed in the
course of assembly by the {\sc Cap3} tool \cite{Huang99}.

@@
